---
title: "LearnRMD"
output:
  html_document:
    css: faded.css
    theme: journal
    toc: yes
  slidy_presentation: default
  beamer_presentation: default
  runtime: shiny
---

# MD EXAMPLE: NasaWeather::atmos

## Data Description

The `atmos` data set resides in the `nasaweather` package of the *R* programming language. It contains a collection of atmospheric variables measured between 1995 and 2000 on a grid of 576 coordinates in the western hemisphere. The data set comes from the [2006 ASA Data Expo](http://stat-computing.org/dataexpo/2006/).

Some of the variables in the `atmos` data set are:

* **temp** - The mean monthly air temperature near the surface of the Earth (measured in kelvins (*K*))

* **pressure** - The mean monthly air pressure at the surface of the Earth (measured in millibars (*mb*))

* **ozone** - The mean monthly abundance of atmospheric ozone (measured in Dobson units (*DU*))

You can convert the temperature unit from Kelvin to Celsius with the formula

$$ celsius = kelvin - 273.15 $$

And you can convert the result to Fahrenheit with the formula

$$ fahrenheit = celsius \times \frac{9}{5} + 32 $$

```{r, echo = FALSE, results = 'hide'}
example_kelvin <- 282.15
```

For example, **r example_kelvin** degrees Kelvin corresponds to **r example_kelvin - 273.15** degrees Celsius.

## Application Example

> Load package & 分組 & 作圖

```{r message= FALSE}
# install.packages("nasaweather")
# install.packages("ggvis")
library("nasaweather")
library("dplyr")
library("ggvis")
```

```{r}
# Set the year variable to 1995
year <- 1995

means <- atmos %>%
  filter(year == year) %>%
  group_by(long, lat) %>%
  summarize(temp = mean(temp, na.rm = TRUE),
         pressure = mean(pressure, na.rm = TRUE),
         ozone = mean(ozone, na.rm = TRUE),
         cloudlow = mean(cloudlow, na.rm = TRUE),
         cloudmid = mean(cloudmid, na.rm = TRUE),
         cloudhigh = mean(cloudhigh, na.rm = TRUE)) %>%
  ungroup()

# Inspect the means variable
means

#plot the temp variable vs the ozone variable
means %>%
  ggvis(x = ~temp, y = ~ozone) %>%
  layer_points()

```

> Modeling 關聯預測

```{r}
# Change the model: base prediction only on temp
mod <- lm(ozone ~ temp, data = means)

# Generate a model summary and interpret the results
summary(mod)
```

looking for the model's estimates for the intercept and temp coefficients, as well as the p-value associated with each coefficient and the model's overall Adjusted R-squared.

## Reporting 報告撰寫
> how to write the narrative sections

## Cleaning

```{r echo = FALSE}
year <- 2005
```

For the remainder of the report, we will look only at data from the year `r year`. We aggregate our data by location, using the *R* code below.

```{r}
means <- atmos %>%
  filter(year == year) %>%
  group_by(long, lat) %>%
  summarize(temp = mean(temp, na.rm = TRUE),
         pressure = mean(pressure, na.rm = TRUE),
         ozone = mean(ozone, na.rm = TRUE),
         cloudlow = mean(cloudlow, na.rm = TRUE),
         cloudmid = mean(cloudmid, na.rm = TRUE),
         cloudhigh = mean(cloudhigh, na.rm = TRUE)) %>%
  ungroup()
```


where the `year` object equals `r year`.

### Ozone and temperature

Is the relationship between ozone and temperature useful for understanding fluctuations in ozone? A scatterplot of the variables shows a strong, but unusual relationship.

```{r fig.height = 4, fig.width = 5, echo=FALSE, warning= F}
means %>%
  ggvis(~temp, ~ozone) %>%
  layer_points()
```

We suspect that group level effects are caused by environmental conditions that vary by locale. To test this idea, we sort each data point into one of four geographic regions:

```{r}
means$locale <- "north america"
means$locale[means$lat < 10] <- "south pacific"
means$locale[means$long > -80 & means$lat < 10] <- "south america"
means$locale[means$long > -80 & means$lat > 10] <- "north atlantic"
```

### Model

We suggest that ozone is highly correlated with temperature, but that a different relationship exists for each geographic region. We capture this relationship with a second order linear model of the form

$$ ozone = \alpha + \beta_{1} temperature + \sum_{locales} \beta_{i} locale_{i} + \sum_{locales} \beta_{j} interaction_{j} + \epsilon$$

This yields the following coefficients and model lines.

```{r}
lm(ozone ~ temp + locale + temp:locale, data = means)
```

```{r fig.height = 4, fig.width = 5, echo=FALSE}
means %>%
  group_by(locale) %>%
  ggvis(~temp, ~ozone) %>%
  layer_points(fill = ~locale) %>%
  layer_model_predictions(model = "lm", stroke = ~locale) %>%
  hide_legend("stroke") %>%
  scale_nominal("stroke", range = c("darkorange", "darkred", "darkgreen", "darkblue"))
```

### Diagnostics

An anova test suggests that both locale and the interaction effect of locale and temperature are useful for predicting ozone (i.e., the p-value that compares the full model to the reduced models is statistically significant).

```{r}
mod <- lm(ozone ~ temp, data = means)
mod2 <- lm(ozone ~ temp + locale, data = means)
mod3 <- lm(ozone ~ temp + locale + temp:locale, data = means)

anova(mod, mod2, mod3)
```

# MD NOTES

## YAML Head

### CSS:

- 創建css檔案放在同一個檔案位置下
- 在html_notebook: 之後
-    css: faded.css (名稱)

### Others

- number_sections: yes 根據##產生數序階層
- toc: yes 出現大鋼

### Markdown

- *italicized* by surrounding it in **asterisks**
- **bold** by surrounding it in two asterisks
- `monospaced` (like code) by surrounding it in **backticks**
- [link]() by surrounding it in hard brackets and then placing the link behind it in parentheses
- * bulleted list in Markdown, 
- * place each item on a new line after an asterisk and a space
- ordered list by placing each item on a new line
- 1. after a number 
- 2. followed by a period 
- 3. followed by a space
`Don't forget to leave a blank line before staring the summation. Otherwise the list will not render correctly.`

##### LaTeX equations
- To embed an equation $1*1=1$ in its own centered equation block, surround the equation with two pairs of dollar signs $$1*1=1$$


## Code chunk

> embed R code into your report. This gives you the best of both worlds: formatted text for narration, and precise R code for reproducible analysis.


### [`knitr` syntax](https://yihui.name/knitr/options/)

> customize each R code chunk in your report by providing optional arguments after the r

- echo = FALSE 讓程式碼不出現(只執行、秀結果)
- eval = FALSE 反過來，只讓Code出現(不執行、沒結果)
`use to display example code that should not be run`
- results = 'hide' 會顯示Code並執行(不秀結果)
- 可以直接給chunk名稱，另外呼叫時用ref.lable='名稱'

### 原則

- It is common to display figures without the code that generates them (the code is a distraction). 通常有圖會關code (`echo`)
- inline **R code**: 如採用`means$locale[1]`結果`r means$locale[1]`
- Each R Markdown document is given a **fresh, empty** R session to run its code chunks in. This means that you will need to define any R objects that this document uses `- and load any packages that it uses -` inside the same R Markdown document. The document won't have access to the objects that exist in your current R session.
- By default, R Markdown will include `message`, `warning` and `error` in your report. We can use options to prevent from displaying these.

## pandoc

> Each R Markdown output template is a collection of knitr and pandoc options. You can customize your output by overwriting the default options that come with the template.

- theme: change the CSS style of HTML output: default, cerulean, journal, flatly, readable, spacelab, united, or cosmo.

- output: export your file as a slideshow:
    + beamer_presentation
    + ioslides_presentation
    + slidy_presentation
    + R Markdown will start a new slide at each first or second level header in your document. You can insert additional slide breaks with Markdown's horizontal rule syntax:

    + `***` Everywhere you add these three asterisks in your text, pandoc will create a new slide.

- to visualize data in a pdf document, you will have to use the **`ggplot2`** package as an alternative to the `ggvis` package. This is for a reason: the ggvis package creates graphs that are `HTML` objects. These graphs are useful for HTML documents, but `cannot be included in a pdf` document without intermediary steps.


# Shiny EXAMPLE

This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately.

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),

  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")

  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Embedded Application

It is also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.

# Shiny EXAMPLE (2)

ggvis provides a number of ways to enhance plots with interacticity. For example, the density plot below allows users to set the kernel and bandwidth of the plot.

```{r echo = FALSE, message = FALSE}
library(ggvis)

mtcars %>% ggvis(x = ~wt) %>%
    layer_densities(
      adjust = input_slider(.1, 2, value = 1, step = .1, label = "Bandwidth adjustment"),
      kernel = input_select(
        c("Gaussian" = "gaussian",
          "Epanechnikov" = "epanechnikov",
          "Rectangular" = "rectangular",
          "Triangular" = "triangular",
          "Biweight" = "biweight",
          "Cosine" = "cosine",
          "Optcosine" = "optcosine"),
        label = "Kernel")
    )
```

## Shiny NOTES

> 在YAML header中加上`runtime: shiny`

- 可用在html及slides上









# Session Info

```{r}
sessionInfo()
```
